\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-24 paper/main.tex
minor changes to fit text in 4 pages

\vspace{0.5ex}\noindent{}The following video demonstrates \tname:

@@

\begin{table}
  \small
  \centering
  \caption{\label{table:bug-interface}\tname command-line interface.}
  \vspace{-1ex}
\begin{tabular}{lp{6.5cm}}
  \toprule
  \textbf{command} & \textbf{description} \\
  \midrule
list-tests & List the tests available on this dataset\\
run-test & Runs one test\\
run-tests & Runs all the tests\\
run-tool & Runs a testing tool in a given buggy environment \\
show-info & Shows information about the tests available on this benchmark\\
stats & Shows statistics about this dataset (e.g., number of tests
that require GPU, number of tests that reproduce bugs in C or Python
code, etc.)\\
\bottomrule
\end{tabular}
  \vspace{-3ex}
\end{table}

@@

% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:
\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
Using bug-id 120903 for library pytorch version 2.2.0
...
RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL 
ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please
report a bug to PyTorch.
====== 1 passed in 1.09s ======
Updating environment in the container of the testing tool
...
Running the testing tool on the environment of the bug
APIs under test:
torch.fake_quantize_per_channel_affine
torch.all
torch.compile
Testing on  ['torch']
torch.atanh
...
No violation of precision-oracle in the compare-bug category
No violation of precision-oracle in the potential-bug category
No violation of cuda-oracle in the compare-bug category
No violation of cuda-oracle in the potential-bug category
No violation of crash-oracle in the compare-bug category
No violation of crash-oracle in the potential-bug category
-> torch.fake_quantize_per_channel_affine did not face any failures
-> torch.all did not face any failures
-> torch.compile did not face any failures
Reproduced 0 out of 3 bugs
\end{lstlisting}

>>>>

\vspace{0.5ex}\noindent{}The video from this URL demonstrates \tname:

@@

\begin{table}
  \small
  \centering
  \caption{\label{table:bug-interface}\tname command-line interface.}
  \vspace{-1ex}
\begin{tabular}{lp{6.5cm}}
  \toprule
  \textbf{command} & \textbf{description} \\
  \midrule
list-tests & List the tests available on this dataset\\
run-test & Runs one test\\
run-tests & Runs all the tests\\
run-tool & Runs a testing tool in a given buggy environment \\
show-info & Shows information about available tests\\
stats & Shows statistics about this dataset (e.g., number of tests
that require GPU, etc)\\
%% number of tests that reproduce bugs in C or Python
%% code, etc.)\\
\bottomrule
\end{tabular}
  \vspace{-3ex}
\end{table}

@@

% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:
\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
Using bug-id 120903 for library pytorch version 2.2.0...
RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL 
ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please
report a bug to PyTorch.
====== 1 passed in 1.09s ======
Updating environment in the container of the testing tool...
Running the testing tool on the environment of the bug
APIs under test:
torch.fake_quantize_per_channel_affine
torch.all
torch.compile
Testing on  ['torch']
torch.atanh...
No violation of precision-oracle in the compare-bug category
No violation of precision-oracle in the potential-bug category
No violation of cuda-oracle in the compare-bug category
No violation of cuda-oracle in the potential-bug category
No violation of crash-oracle in the compare-bug category
No violation of crash-oracle in the potential-bug category
-> torch.fake_quantize_per_channel_affine did not face any failures
-> torch.all did not face any failures
-> torch.compile did not face any failures
Reproduced 0 out of 3 bugs
\end{lstlisting}
